NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-08-10 paper/Chapters/Chapter2.tex
methods DM removed

\begin{enumerate}
	\item The crude association between the carbohydrate eating groups and the outcomes was first examined. 
	\item Potential confounders of the association between carbohydrate eater groups (exposure) and the outcomes were selected depending on the descriptive statisitics conducted above, ie. those are associated with both the exposure and the outcome and not on the causal pathway were selected as potential confounders. Those are strongly related with the outcomes but may not associated with carbohydrate eating groups may reduce the standard errors and so improve the precisions are also considered. 
	\item Confounding and/or interaction effect from each of the potential factors were checked one by one. 
	\item A preliminary model that includes all of the variables suggested to be confounders in the previous step was established. 
	\item The remaining variables were added to the preliminary model one by one to see if any of them may be a confounder in condition of the presence of the other covariates. 
	\item For logistic regression models under survey data, goodness-of-fit (calibration) was assessed using the adapted \code{svylogitgof} command in Stata \parencite{archer2006goodness}. Other diagnostics for regular logistic regression models, such as estimating the pseudo-R\textsuperscript{2},  AIC or BIC, checking the standardized Pearson residuals, or covariate pattern residuals are currently not available for weighted survey data. 
	\item For linear regression models (WC, BMI), assumption of independent observations is violated as soon as we weighted the sample. General checking such as QQ plots of the residuals (normality), plotting the residuals against fitted values (constant variance) are not available as well. Outliers, leverage, and Cook's distance cannot be check either, however, samples with extreme weightings (if exist) are checked by removing them and refit the models as a sensitivity analysis.
	\item Since under survey design data, the sampling-weighted least squares are not maximum likelihood, it would not be possible to compare models using likelihood ratio test. Instead, adjusted Wald tests with $p < 0.05$ were used as criteria for variable inclusion in the final model, and a useful tool to decide whether quadratic and cubic terms of continuous variables are necessary in improving the fitting of model. 
\end{enumerate}

>>>>

\begin{enumerate}
	\item The crude association between the carbohydrate eating groups and the outcomes was first examined. 
	\item Potential confounders of the association between carbohydrate eating groups (exposure) and the outcomes were selected depending on the descriptive statisitics conducted above, i.e. those are associated with both the exposure and the outcome and also not on the causal pathway were selected as potential confounders. Those are strongly related with the outcomes but may not associated with carbohydrate eating groups may reduce the standard errors and so improve the precisions are also considered. 
	\item Confounding and/or interaction effect from each of the potential factors were checked one by one. Interaction effect were tested using the adjusted Wald test comparing models with and without the interaction terms.  
	\item A preliminary model that includes all of the variables suggested to be confounders in the previous step was established. 
	\item The remaining variables were added to the preliminary model one by one to see if any of them may be a confounder in condition of the presence of the other covariates. 
	\item For logistic regression models (hypertension) under the survey data, goodness-of-fit was assessed using the adapted \code{svylogitgof} command in Stata \parencite{archer2006goodness}. Other diagnostics for regular logistic regression models, such as estimating the pseudo-R\textsuperscript{2},  AIC or BIC, checking the standardized Pearson residuals, or covariate pattern residuals are currently not available for weighted survey data. 
	\item For linear regression models (WC, BMI), assumption of independent observations is violated as soon as we weighted the sample. General checking such as QQ plots of the residuals (normality), plotting the residuals against fitted values (constant variance) are not available as well. Outliers, leverage, and Cook's distance cannot be check either, however, samples with extreme weightings (if exist) were checked by removing them and refit the models as a sensitivity analysis.
	\item Since under survey design data, the sampling-weighted least squares are not maximum likelihood, it would not be possible to compare models using likelihood ratio test. Instead, adjusted Wald tests with $p < 0.05$ were used as criteria for variable inclusion in the final model. Another Stata command \code{linktest} was also used to  decide whether quadratic and cubic terms of continuous variables were necessary in improving the fitting of model \parencite{pregibon1980goodness}. 
\end{enumerate}
